---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# animeR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/animeR)](https://CRAN.R-project.org/package=animeR)
<!-- badges: end -->

## Purpose 

The goal of animeR is to help anime directors and anime lovers to understand the current trend in the anime industry. The package builds on the dataset Anime.csv which includes information about over 20,000 different animes, such as their name, time aired, producers, genres, synopsis, score, popularity, and more. Our goal for this package is to provide tools for anime lovers and directors to easily filter for their desired criteria, understand recurring themes, and predict the popularity of a anime.

## Target Audience

Our target audience would be people interested in anime or newly exploring anime who may be looking for detailed anime information and/or recommendations, and creative professionals, such as directors and people who works in anime or media industry, who want to understand the trends in their industry.

## Installation

You can install the development version of animeR like so:

``` r
devtools::install_github("cbasnetchettri/animeR")
library(animeR)
```

## Project Proposal

1) `search_anime(...)`: This function serves as a tool to obtain an overview of  filtering tool for anime lovers to locate the list of anime of their interest. 

2) `anime_rec(x, y)`:  The function takes in genre x and year y and output a list of five anime with their synopsis based on popularity rating.

3) `get_trend(x, y)`: This function takes in genre x and year y and output a wordcloud that shows the most recurring themes and words in the anime’s synopsis. 

4) `info( )`: This function returns the top five anime of all time based on popularity, the visualization of anime popularity by genre, and number of anime by top producers using a bar chart. 

5) `predict_popularity( )`: this function fits a multiple regression model predicting the popularity rating of an anime based on categorical variables like the Source of the anime. Also, this function conducts model analysis to help anime directors and investors to predict the popularity of a potential anime. 


## Example

This is a basic example for `search_anime()`:

```{r example}
library(animeR)

# Search all the anime that has "Naruto" in their title. Please make sure to have a character as an input.
search_anime("Naruto")
```


## Group Members 

- Charavee Basnet Chettri 
- Michiru Nozawa
- Lily Diao
