---
title: "animeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{animeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(animeR)
```

The `animeR` is a package that contains the detailed information of more than 20000 anime. 

## Motivation

The goal of `animeR` is to help anime directors and anime lovers to easily understand the current  in the anime industry. The package builds on the dataset. 

## Dataset

The dataset `anime` is taken from [Kaggle](https://www.kaggle.com/datasets/harits/anime-database-2022). Based on Kaggle, the data was collected through web scraping sourced by [MyAnimeList.net](https://myanimelist.net/) and teh data of 21460 anime were obtained and contained in the dataset `anime`. 

## Who should use this package?

This package would be perfect for not only people who are already interested in anime but also those who are newly exploring anime and are looking for detailed anime information and/or recommendations. Moreover, creative professionals, such as directors and people who works in anime or media industry, can use this package to understand the s in their industry. 

## What does the data look like?

Here is the first five rows of `anime` dataset. 

```{r}
head(anime)
```

## What can we do with this data?

These are the some example questions that we can address: 

1. Is there any anime that is related to One Piece?  

2. What are the top 5 most popular original Sci-Fi anime? 

3. What are the top 20 most popular anime of all time?

4. How are animes scored based on the source they are made from and their rating?

5. What are some current s in the anime industry ?

6. What are the most common themes in an anime synopsis?

7. What are the score distributions across different anime sources?
   

### Example 1

**Is there any anime that is related to One Piece?**

Many anime have multiple series, spin offs, and movies, so sometimes it is hard to find the particular anime that you are looking for. In this kind of situation, you can use the `search_anime()` function. For instance, if you are looking for One Piece anime, you can input “One Piece” as your input.

```{r}
search_anime("One Piece")
```

### Example 2

**What are the top 5 most popular original Sci-Fi anime?**

We can use the `anime_rec()` function to find the 5 most popular Sci-Fi anime that are based on original stories. Here, we can obtain not only the name of those anime but also their synopsis and rating. The output is clear and easy to interpret since it is ordered based on the popularity. If you are interested in other genres or sources, `unique_list()` function will give you all the other possible genres and sources that you can use for the input. 

```{r}
# Check the list of genres
unique_list("genres")
```

```{r}
# Check the list of sources
unique_list("sources")
```

```{r}
# Find top 5 original sci-fi anime
anime_rec("Sci-Fi", "Original", 5)
```


### Example 3

**What are the top 20 most popular anime of all time?**

If we, as a curious user, are not sure about which anime to start watching, we can obtain the top 20 list of the most popular anime along with each anime’s quick information to be able to decide better. Quick information includes the genre, source, rank and rating. If we, as a new creator, want some direction and understanding of what kind of anime has been the most popular based on its genre and source, this function can prove helpful.

```{r}
# Find top 20 most popular anime
rank_popular(20)
```

### Example 4

**How are animes scored based on the source they are made from and their rating?**

We can use this function, which generates a side-by-side boxplot comparing the median scores and outliers of PG-13 rated anime for each type of source, to enhance our understanding of anime and especially inform creators about what source they can explore for their potential anime to also achieve better scores. 

```{r}
# Compare Score boxplot statistics of each Source given the rating
score_source_byrating ("PG-13")
```

### Example 5

**What is the current  in the anime industry ?**

For directors who are interested in the current  in the anime industry, they might be interested in learning about how long most anime are, what are the top producers and the score distribution of their animes, and what genre tends to get a higher score. These users can use the `get_(inpute_theme)` function to present the distribution of anime duration, anime score across different producers, and average anime score across all genres. 

```{r, warning=FALSE, fig.width=7.5, fig.height=4}
get_trend("Movie")
```

### Example 6

**What are the most common themes in anime synopsis?**

For directors and screenwriters who are interested in learning about the most common themes in the synopsis, we provide a word cloud visualization that makes it easier for users to see what are the most prevalent ideas in an anime's plot. They can use the `get_(input_theme)` to see all common themes in a visualization.

```{r, warning=FALSE, message=FALSE}
get_theme("Movie")
```



